Markov Chain
========================


**Bibliography**

http://alexhwoods.com/2015/09/05/markov-chains-in-r/

http://math.stackexchange.com/questions/587559/forming-the-transition-matrix-for-markov-chain-given-a-word-description-of-tran

https://cran.r-project.org/web/packages/markovchain/vignettes/markovchainCrashIntro.pdf


Suppose a car rental agency has three locations in Ottawa: Downtown location (labeled A), East end location (labeled B) and a West end location (labeled C). The agency has a group of delivery drivers to serve all three locations. The agency's statistician has determined the following:

* 1.      Of the calls to the Downtown location, 30% are delivered in Downtown area, 30% are delivered in the East end, and 40% are delivered in the West end

* 2.      Of the calls to the East end location, 40% are delivered in Downtown area, 40% are delivered in the East end, and 20% are delivered in the West end

* 3.      Of the calls to the West end location, 50% are delivered in Downtown area, 30% are delivered in the East end, and 20% are delivered in the West end.



After making a delivery, a driver goes to the nearest location to make the next delivery. This way, the location of a specific driver is determined only by his or her previous location.
 
We model this problem with the following matrix:


```{r, cache=TRUE}

library(markovchain)




#markovchainFit Function to return fitted Markov chain for a given sequence.
#predict Method to calculate predictions from markovchain or markovchainList objects.
#rmarkovchain Function to sample from markovchain or markovchainList objects.


## Steps: 
#1.Create matrix from sequence (frecuency and probability)
#2.Fit model 
#3.Predict new action from a current state

`````


```{r, sintetic_data, cache=TRUE}

##### EXAMPLE syntetic data

rentalStates <- c("Downtown", "East", "West")
rentalTransition <- matrix(c(0.3, 0.3, 0.4, 
                      0.4, 0.4, 0.2, 
                      0.5, 0.3, 0.2),
                      byrow = T, nrow = 3, dimnames = list(rentalStates, rentalStates))

rentalTransition

# 
# > rentalTransition
#          Downtown East West
# Downtown      0.3  0.3  0.4
# East          0.4  0.4  0.2
# West          0.5  0.3  0.2


mcRental <- new("markovchain", states = rentalStates, byrow = T, 
                transitionMatrix = rentalTransition, name = "Rental Cars")



# > mcRental
# Rental Cars 
#  A  3 - dimensional discrete Markov Chain with following states 
#  Downtown East West 
#  The transition matrix   (by rows)  is defined as follows 
#          Downtown East West
# Downtown      0.3  0.3  0.4
# East          0.4  0.4  0.2
# West          0.5  0.3  0.2



# We can access the transition matrix just by calling the mc object
mcRental[1]  # the probabilities that we go Downtown, East, and West, given that we are currently Downtown

plot(mcRental)  # we can plot it

transitionProbability(mcRental, "Downtown", "West")   # the prob that a driver will go from downtown to West

# Here is a question to set up some of the functions 
# Given we are downtown, what is the probability we will be downtown in two trips?
# We can go Downtown -> Downtown, 
a <- 0.3 * 0.3

# East -> Downtown (note that to we have to get the probability of going Downtown from the East location),
b <- 0.3 * 0.4

# West -> Downtown (same logic here)
c <- 0.4 * 0.5

a + b + c    # The probability that we will be downtown in 2 trips.

# That isn't something you want to be doing, especially if you want the probabilities after 20 trips.
# In turns out though, we can get the same results by squaring the matrix.
mcRental ^ 2

# We can do this for any number of trips, where the number of trips is the exponent.
mcRental ^ 20   # notice how where you are starts to become irrelevant, as the number of trips increases.

# It's also important to note that the transition matrix T ^ n, will converge as n increases, 
# given that there are no 0's or 1's in our initial matrix.


# So if we had 70 drivers, how many drivers would be at the West location after 30 trips?
# This distribution, the converged probabilities of each state, where the location at which you start
# is irrelevant (because n is sufficiently large), is called the stationary distribution.
# We can access it using the steadyStates() method.
mcRental ^ 30
70*steadyStates(mcRental)      



# Now let's look at some of the other methods that the markovchain package has
summary(mcRental)
conditionalDistribution(mcRental, "Downtown")



mcRental[2,3]

# > mcRental
# Rental Cars 
#  A  3 - dimensional discrete Markov Chain with following states 
#  Downtown East West 
#  The transition matrix   (by rows)  is defined as follows 
#          Downtown East West
# Downtown      0.3  0.3  0.4
# East          0.4  0.4  0.2
# West          0.5  0.3  0.2



#It is possible to simulate states distribution after n-steps

initialState<-c(0,1,0)
steps<-4
finalState<-initialState*mcRental^steps #using power operator
finalState


#As well as steady states distribution
steadyStates(mcRental) #S4 method


````



```{r, fromSequencyData, cache=TRUE}

## SEQUENCIES


library(markovchain) 
sequence <- c("nomina","recibos","hipoteca", "ppi", "recibos", "hipoteca", "prestamo", "wallet", "wallet") 

#sequence1 <- c( "a", "a", "b", "a", "b", "a", 
#              "b", "a", "a", "b", "b", "b", "a,b", "a,b", "a", "a,b", "b")

mcFit <- markovchainFit(data=sequence)
mcFit

mcFit$estimate

#### converts a sequence matrix into a probability matrix
createSequenceMatrix(sequence)

createSequenceMatrix(sequence, toRowProbs = TRUE, sanitize = TRUE)

## a.ahead (numero de acciones posteriores al estado indicado en newdata)
predict(mcFit$estimate, newdata="recibos",n.ahead=1)




seq <- createSequenceMatrix(sequence)
seq <- prop.table(seq,1)
seq[complete.cases(seq), ]
seq[is.na(seq)] <- 0
seq

#mc <- new("markovchain", states= colnames(seq), byrow=T,  
#                transitionMatrix = as.matrix(seq),
#          name = "Sequence example"
#          )


prop.table(seq,1)
mc <- new("markovchain", states = colnames(seq), byrow = T, 
                transitionMatrix = seq, name = "Productos")

plot(mc)
`````

```{r, realdata_easy, cache=TRUE, EVAL=FALSE}


## REAL DATA (i)

#columns
Actions <- c("Hipoteca", "Prestamo", "Nomina", "Recibo")

## Define K lenght states (rows)
States <- c("Nomina-Recibo", "Alta-txc", "txc-recibo", "txc-nomina")



Transition <- matrix(c(1,0,0,0, 
                      0,0,0,1, 
                      2,0,0,0,
                      0,1,0,0),
                      byrow = T, nrow = 4, dimnames = list(States, Actions))

Transition



# mc <- new("markovchain", states = States, byrow = T, 
#                 transitionMatrix = Transition, name = "BBVA Engagement")
# 
# 
# 
# # We can access the transition matrix just by calling the mc object
# mc[1]  # the probabilities that we go Downtown, East, and West, given that we are currently Downtown
# 
# plot(mc)  # we can plot it
# 
# transitionProbability(mc, "Nomina-Recibo", "Prestamo")   # the prob that a driver will go from downtown to West



`````

```{r, realdata_realinput_sequence_tests, cache=TRUE}

## REAL DATA (ii)


#### 1. INPUT:
# 
# CCLIENT    DATE     PRODUCTO(state)
# 3         1983      nomina
# 3         1984      recibos
# :
# :
# 58997     1983      recibos
# 58997     1984      hipoteca
# :
  

##### 2. COMPUTE FRECUENCY TRANSITION MATRIX FROM SEQUENCE

set.seed(1001)

# Raw data in long format --
raw <- data.frame(name=c("f1","f1","f1","f1","f2","f2","f2","f2"),
                  year=c(83,   84,  85,  86,  83,  84,  85,  86),
                  state=c("nomina","recibos","hipoteca", "hipoteca", "recibos", "hipoteca", "prestamo", "wallet")  )

transition.probabilities <- function(D, timevar="year",
                                     idvar="name", statevar="state") {
  merged <- merge(D, cbind(nextt=D[,timevar] + 1, D),
  by.x = c(timevar, idvar), by.y = c("nextt", idvar))
  t(table(merged[, grep(statevar, names(merged), value = TRUE)]))
}

p <- transition.probabilities(raw, timevar="year", idvar="name", statevar="state")

# > p
#           state.x
# state.y    hipoteca nomina prestamo recibos wallet
#   hipoteca        1      0        1       0      0
#   nomina          0      0        0       1      0
#   prestamo        0      0        0       0      1
#   recibos         2      0        0       0      0
#   wallet          0      0        0       0      0



probabilities_p <- p

probabilities_p[] <- as.vector(p) / rep( as.vector(apply( p, 2, sum )), each=dim(p)[1] )




###########  FRECUENCY MATRIX TO PROBABILITY 



# Sample data
states <- sample(LETTERS[1:3], 1e5, replace=TRUE)

# Pairs of transitions
d <- embed( states, 3 )
colnames(d) <- c("today", "yesterday", "day before yesterday")
head(d)

# Count the transitions
counts <- table( as.data.frame( d ) )

# Divide by the total number of transitions, to have probabilities
probabilities <- counts
probabilities[] <- as.vector(counts) / rep( as.vector(apply( counts, 2:3, sum )), each=dim(counts)[1] )

# Check that the probabilities sum up to 1
apply( probabilities, 2:3, sum )

# Convert the 3-dimensional array to a data.frame
library(reshape2)
dcast( melt( probabilities ), yesterday + `day before yesterday` ~ today )



##########





```