Survival analysis
====================

Bibliografía:

http://www.mas.ncl.ac.uk/~nmf16/teaching/mas3311/practical1.html

**Introduction**

Survival analysis is a set of statistical methods for analyzing the occurrence of events over time. It is also used to determine the relationship of co-variates to the time-to-events, and accurately compare time-to-event between two or more groups. For example:

* Time to death in biological systems.
* Failure time in mechanical systems.
* How long can we expect a user to be on a website / service?
* Time to recovery for lung cancer treatment.


The statistical term 'survival analysis' is analogous to 'reliability theory' in engineering, 'duration analysis' in economics, and 'event history analysis' in sociology.

The **two key functions** in survival analysis are the survival function and the hazard function:

* The **survival function**, conventionally denoted by SS, is **the probability that the event (say, death) has not occurred yet**:

S(t)=Pr(T>t),

where TT denotes the **time of death** and PrPr the probability. Since SS is a probability, 0≤S(t)≤10≤S(t)≤1. 

Survival times are non-negative (T≥0T≥0) and, generally, S(0)=1S(0)=1.

* The **hazard function** h(t)h(t) is the **event (death) rate at time tt**, conditional on survival until tt (i.e., T≥tT≥t):

h(t)=limΔt→0Pr(t≤T≤t+Δt|T≥t)=limΔt→0Pr(t≤T≤t+Δt)S(t)=p(t)S(t),

where pp denotes the probability density function.

In practice, we do not get to observe the actual survival function of a population; we must use the observed data to estimate it. A popular estimate for the survival function S(t)S(t) is the Kaplan–Meier estimate:

Ŝ (t)=∏ti≤tni−dini,

S^(t)=∏ti≤tni−dini,

where didi is the number of events (deaths) observed at time titi and nini is the number of subjects at risk observed at time titi.



**Censoring**

Censoring is a type of missing data problem common in survival analysis. Other popular comparison methods, such as linear regression and t-tests do not accommodate for censoring. This makes survival analysis attractive for data from randomized clinical studies.

In an ideal scenario, both the birth and death rates of a patient is known, which means the lifetime is known.
Right censoring occurs when the 'death' is unknown, but it is after some known date. e.g. The 'death' occurs after the end of the study, or there was no follow-up with the patient.
Left censoring occurs when the lifetime is known to be less than a certain duration. e.g. Unknown time of initial infection exposure when first meeting with a patient.



**Estimating survival with Kaplan-Meier**

The simplest fit estimates a survival object against an intercept. However, the survfit() function has several optional arguments. For example, we can change the confidence interval using conf.int and conf.type.
See help(survfit.formula) for the comprehensive documentation.

`````{r, cache=TRUE}
library(survival)
library(KMsurv)

#SMALL DATA SET
my.times <-c(10,13,18,19,23,30,36,38,54,56,59,75,93,97,104,107,107,107)
my.events <-c(1,0,0,1,0,1,1,0,0,0,1,1,1,1,0,1,0,0)
my.surv <- Surv(my.times,my.events)
my.surv

my.KMest <- survfit(my.surv~1, conf.int=0.95)
plot(my.KMest)
summary(my.KMest)
`````

``````{r}

## LUNG DATA

head(lung)
names(lung)

#Sometimes we want to compare two or more different subgroups of a single data frame. For example, we might wan to compare the survivor functions for males and females in the lung data set. To do this, create a Surv object for the lung data:

s <- Surv(lung$time, lung$status)

#Then fit the KM estimate, telling R to split the data up according to the sex of each individual:
lung.KM <- survfit(s~lung$sex)
lung.KM<-survfit(s~sex,data=lung)

plot(lung.KM)
summary(lung.KM)

`````







``````{r, eval=FALSE}

######## Nonparametric Estimation #########

## We will revisit "survfit" R function introduced before and explore 
## more function options. 

#setwd('c:/work/teaching/math434/fall09')
library(survival)
library(KMsurv)
bfeed=read.table("bfeeddata.txt",header=T) 
bfeed
## This is the breast feeding data.

## Kaplan-Meier (PL) estimate, the standard error and 
## log-log type of pointwise confidence interval.
fit1=survfit(Surv(time,ind)~1,data=bfeed,conf.type='log-log')
summary(fit1)
## check the varibles listed in the survfit object. 
attributes(fit1)

## Plot the estimation without confidence interval.
plot(fit1,conf.int=0)

## Compare different type of confidence intervals.
plot(fit1,xlab="Weeks",ylab="Survival Probability",main='Kaplan-Meier Estimate')
fit2=survfit(Surv(time,ind)~1,data=bfeed,conf.type='plain')
lines(c(0,fit2$time),c(1,fit2$lower),type='s',col=2,lty=2)
lines(c(0,fit2$time),c(1,fit2$upper),type='s',col=2,lty=2)
## Note that the default "log" transformation in R is different 
## from the "log" transformation mentioned in the textbook. 
## It is g(t)=log(t)
fit3=survfit(Surv(time,ind)~1,data=bfeed,conf.type='log')
lines(c(0,fit3$time),c(1,fit3$lower),type='s',col=3,lty=3)
lines(c(0,fit3$time),c(1,fit3$upper),type='s',col=3,lty=3)
legend(130,1,legend=c("'log-log' CI","'linear' CI","'log' CI"),col=1:3,lty=1:3)

## All CIs are close to each other.

## The "survfit" function in R does not produce confidence bands.
## Here is a function to creat confidence bands.
source('surv.cband.R')
cband=surv.conf.bands(fit1,dim(bfeed)[1]) 
3.1622
## Now let's add the 95% EP log-log confidence band on the previous plot
lines(c(0,cband$time),c(1,cband$lower),type='s',col=4,lty=4)
lines(c(0,cband$time),c(1,cband$upper),type='s',col=4,lty=4)

## Produce the Figure 4.5 in example 4.2 on page 112.
data(bmt)
## This is bone marrow transplant for Leukemia data .
fit4=survfit(Surv(t2,d3)~1,data=bmt[bmt$group==1,],conf.type='plain')
fit4ep=surv.conf.bands(fit4,sum(bmt$group==1),conf.type='plain',tL=100,tU=600) 
2.8826
fit4hall=surv.conf.bands(fit4,sum(bmt$group==1),conf.type='plain',type='hall',tL=100,tU=600) 
1.3211
plot(fit4,xlim=c(100,600),xlab='Days Post Transplant',
  ylab='Estimated Survival Function',main="Reproducing Figure 4.5")
lines(c(0,fit4ep$time),c(1,fit4ep$lower),type='s',col=3,lty=3)
lines(c(0,fit4ep$time),c(1,fit4ep$upper),type='s',col=3,lty=3)
lines(c(0,fit4hall$time),c(1,fit4hall$lower),type='s',col=4,lty=4)
lines(c(0,fit4hall$time),c(1,fit4hall$upper),type='s',col=4,lty=4)
legend(400,1,c('KM estimate','CI','EP band','Hall-Wellner band'),col=c(1,1,3,4),lty=1:4)


## Another possible estimate is Fleming-Harrington estimate, 
## which we will discuss more in detail in semiparametric models.
fit5=survfit(Surv(time,ind)~1,data=bfeed,type='fh2',conf.type='plain')
## or equivalently you may write as
fit5=update(fit1,type='fh2',conf.type='plain')

## Nelson-Alen estimator for cumulative hazard, the standard error and
## linear type of pointwise confidence interval.
Hhat=-log(fit4$surv)
Htilde=cumsum(fit4$n.event/fit4$n.risk)
plot(fit4$time,Hhat,type='s',
	xlim=c(100,600),xlab='Days Post Transplant',
	ylab='Estimated Cumulative Hazard Rate')
lines(fit4$time,Htilde,type='s',lty=2,col=2)
legend(100,1,c('KM estimate','NA estimate'),lty=1:2,col=1:2)

## Median lifetime and its confidence interval could be found in the output directly.
fit1
fit4

## Mean lifetime and its confidence interval.
print(fit1,print.rmean=TRUE)
print(fit4,print.rmean=TRUE)


######## Nonparametric Tests #########

## Two-sample comparison
 
library(KMsurv)
data(btrial)
## This is the data in the Breast-Cancer Trial (Chap1.5)
## Log-rank test
survdiff(Surv(time,death)~im,data=btrial)
## Peto-Peto modified Gehan-Wilcoxon test
survdiff(Surv(time,death)~im,data=btrial,rho=1)

## Check the R function
survdiff

## A traditional Wilcoxon Test: wilcox.test

## Example 7.2 on page 209
library(KMsurv)
data(kidney)
logrank=survdiff(Surv(time,delta)~type,data=kidney)
logrank$var # variance-covariance matrix 

## Could you write a R function to carry the traditional Gehan-Wilcoxon Test?


## More-sample comparison
## Exampe 7.4 on page 272
data(bmt)
logrank2=survdiff(Surv(t2,d3)~group,data=bmt,rho=0)
logrank2
logrank2$var


## Stratified test
## Example 7.7 on page 220

## The dataset on the textbook website (and in R) is different from the dataset in the textbook on page 12. 
## Here we correct the dataset so that we have the exact the same dataset as in the textbook.
## Further more, there are typos in the example 7.7. 
## " The stratified log-rank test is.... 0.3627 which has a p-value of 0.7169."
## "...if we perform test only on Hodgkin's disease patients, 
## we find that the test statistic has a value of 2.52 (p=0.0117),"

data(hodg)
hodg[23,]=c(2,1,176,1,80,38)
testdiff=survdiff(Surv(time,delta)~gtype+strata(dtype),data=hodg,rho=0)
testdiff$obs-testdiff$exp
testdiff$var
## Comparing "testdiff" with the test within each strata,
survdiff(Surv(time,delta)~gtype,data=hodg[hodg$dtype==1,],rho=0)
survdiff(Surv(time,delta)~gtype,data=hodg[hodg$dtype==2,],rho=0)
## Comparing "testdiff" with the test ignoring the disease type,
survdiff(Surv(time,delta)~gtype,data=hodg,rho=0)


``````